---
title: "my-first-document"
format: html
editor: visual
author: Markus
table-of-contents: true
---

This document is all about my previous experience with writing and publishing.

## What gave me joy

-   making progress in writing code (R)

-   planning of the publication in a team (brainstorming sessions)

-   some parts of the writing itself

## What I found challenging

-   since I joined the project at a later stage: getting into the work other had previously done

-   learning how to use new tools (Git/GitHub, Overleaf, ...)

## What I want to learn

-   using quarto files to create documents that contain both code and text (and graphs)

## The rest is irrelevant

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
